\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-30 OaklandSubmission/main.tex
abstract

  %While the application and potential impact of secure computation is virtually limitless, writing an efficient and scalable secure protocol is by no means an easy feat.
% Prior work in designing such protocols, suffered from either a) a lack of programmability (e.g. requiring the programmer to write cryptography-aware circuits for the computation); b) a lack of efficiency for several natural computations (such as machine learning classification tasks); or c) required cryptographers to design hand-crafted protocols for various applications.
We present \tool: a 
%new ``cryptographic-cost aware'' 
secure two-party computation (\mpc) framework that generates efficient
and scalable
\mpc protocols from high-level, easy-to-write programs.
%% that 
%% %contain absolutely no cryptographic details. Programs in our language 
%% are easy-to-write and are statically verified. 
%Furthermore,
\tool provides formal correctness and security guarantees, and we
empirically demonstrate that the
protocols generated by our framework match or outperform (up to
19x in some cases)
recent works that provide hand-crafted protocols for various
functionalities such as classification and matrix factorization
%% (up to
%% a 19x factor!).
\end{abstract}
\IEEEpeerreviewmaketitle

>>>>

  %While the application and potential impact of secure computation is virtually limitless, writing an efficient and scalable secure protocol is by no means an easy feat.
% Prior work in designing such protocols, suffered from either a) a lack of programmability (e.g. requiring the programmer to write cryptography-aware circuits for the computation); b) a lack of efficiency for several natural computations (such as machine learning classification tasks); or c) required cryptographers to design hand-crafted protocols for various applications.
We present \tool: a 
%new ``cryptographic-cost aware'' 
secure two-party computation (\mpc) framework that generates efficient
and scalable
\mpc protocols from high-level, easy-to-write programs.
\tool provides formal correctness and security guarantees while maintaining performance and scalability.
%% that 
%% %contain absolutely no cryptographic details. Programs in our language 
%% are easy-to-write and are statically verified. 
%Furthermore,
All previous works generate protocols that use either arithmetic or boolean circuits exclusively. Our compiler is the first to generate protocols that combine both arithmetic and boolean  for better performance.
%We give the first compiler that generates protocols which combine both arithmetic and boolean circuits
%for better performance compared to protocols that use either arithmetic or boolean circuits exclusively.
We
empirically demonstrate that the
protocols generated by our framework match or outperform (up to
19x)
recent works that provide hand-crafted protocols for various
functionalities such as secure neural net prediction (Liu et al. CCS'17) and matrix factorization (Nikolaenko et al. CCS'13).
%\tool provides formal correctness and security guarantees.
%% (up to
%% a 19x factor!).
\end{abstract}
\IEEEpeerreviewmaketitle
